---
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: 
      collapsed: true
    number_sections: false
    theme: yeti
params:
  title: ""
  author: ""
  date: !r format(Sys.time(), '%d %B, %Y')
  document: NULL
  render_functions: NULL
  render_section: NULL
  number_sections: TRUE
  debug: FALSE
  out_html: ""
title: "`r params$title`"
author: "`r params$author`"
date: "`r params$date`"
---

<script type="text/javascript">
    $(document).ready(function() {
      $items = $('div#TOC li');
      $items.each(function(idx) {
        num_ul = $(this).parentsUntil('#TOC').length;
        $(this).css({'text-indent': num_ul * 10, 'padding-left': 0});
      });

    });
</script>

<style>
.main-container {
  max-width: 1240px;
  margin-left: auto;
  margin-right: auto;
}

#TOC {
  margin: 25px 0px 20px 0px;
}
@media (max-width: 768px) {
#TOC {
  position: relative;
  width: 100%;
}
}


.toc-content {
  padding-left: 30px;
  padding-right: 40px;
}

div.main-container {
  max-width: 1500px;
}

div.tocify {
  width: 40%;
  max-width: 360px;
  max-height: 85%;
}

@media (min-width: 768px) and (max-width: 991px) {
  div.tocify {
    width: 25%;
  }
}

@media (max-width: 767px) {
  div.tocify {
    width: 100%;
    max-width: none;
  }
}

.tocify ul, .tocify li {
  line-height: 20px;
}

.tocify-subheader .tocify-item {
  font-size: 0.90em;
  padding-left: 25px;
  text-indent: 0;
}

.tocify .list-group-item {
  border-radius: 0px;
}

</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# knitr::opts_knit$set(root.dir = "..")
```


```{r results='asis'}
if (params$debug) {
  cat("# Debug\n")
  cat("## Module structure\n")
  cat("<pre>\n")
  print(params$test)
  cat("</pre>\n")
}
```


```{r}
# DEBUG:
# cat(out, sep="\n")
```


```{r, results='asis'}
cat('<div>',
    params$out_html, 
    '</div>',
    sep="\n")
```


<!--
<script type="text/javascript">
  // When the document is fully rendered...
  $(document).ready(function() {
    // ...select all header elements...
    $('h1, h2, h3, h4, h5').each(function() {
      // ...and add an id to them corresponding to their 'titles'
      $(this).attr('id', $(this).html());
    });
  });
</script>
-->

